Pythran: Turning Python Modules into Optimized C++ Meta-Programs

### 2013-10-02 doc/papers/cc2014/paper.tex
Slightly update tool paper

    This paper presents the optimization techniques the Pythran compiler applies
    to Python code: unboxing, deforestation, inter procedural constant folding,
    explicit and implicit parallelization and implicit vectorization.

>>>>

    This tool paper presents the optimization techniques the Pythran compiler
    applies to Python code: unboxing, deforestation, inter procedural constant
    folding, explicit and implicit parallelization and implicit vectorization.

### 2013-10-02 doc/papers/cc2014/tool.tex
Slightly update tool paper

\bibliographystyle{splncs}
\lstset{language=python,morekeywords={cimport, cdef, with},
basicstyle=\ttfamily, keywordstyle=\bf, stringstyle=\color{gray},
captionpos=b}

@@

\section{Tool Paper Motivation}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{pythran-notebook}
    \caption{Example of IPython Notebook.}
    \label{fig:notebook}
\end{figure}

@@

\begin{lstlisting}
>>> from pythran import passmanager, analysis
>>> pm = passmanager.PassManager("tutorial_module")
>>> code = '''
def foo(l,a):
  l+=[a]
def bar(g):
  foo(g, 1)'''
>>> tree = ast.parse(code)
>>> ae = pm.gather(analysis.ArgumentEffects, tree)
>>> foo, bar = tree.body
>>> ae[foo]
[True, False]
>>> ae[bar]
[True]
\end{lstlisting}

@@

\begin{lstlisting}
>>> code = '''
def foo(c, d):
    b= c or d
    return b'''
>>> tree = ast.parse(code)
>>> al = pm.gather(analysis.Aliases, tree)
>>> returned = tree.body[-1].body[-1].value
>>> print ast.dump(returned)
Name(id='b', ctx=Load())
>>> sorted(a.id for a in al[returned].aliases)
['c', 'd']
\end{lstlisting}

@@

Python Benchmarks is a project that aims at comparing the existing approaches to
speedup numerical computations in Python. The project and its result can be
found on \url{https://github.com/numfocus/python-benchmarks}.
Figure~\ref{fig:python-benchmarks} illustrates the result of one of the
benchmark, showing that Pythran performs well compared to existing approaches.

\begin{figure}

    \includegraphics[width=\textwidth]{rosen_der_logscale}
    \caption{Timings for the \texttt{rosen\_der} function from Python Benchmarks.}
    \label{fig:python-benchmarks}

>>>>

\lstset{language=python,morekeywords={cimport, cdef, with},
basicstyle=\ttfamily, keywordstyle=\bf, stringstyle=\color{gray},
captionpos=b}

@@

\section*{Tool Paper Motivation}

@@

\begin{figure}
    \vspace{-1em}
    \includegraphics[width=\textwidth]{pythran-notebook}
    \caption{Example of IPython Notebook.}
    \label{fig:notebook}
    \vspace{-1em}
\end{figure}

@@

\begin{lstlisting}
>>> from pythran import passmanager, analysis
>>> pm = passmanager.PassManager("tutorial_module")
>>> code = '''
def foo(l,a):
  l+=[a]
def bar(g):
  foo(g, 1)'''
>>> tree = ast.parse(code)
>>> ae = pm.gather(analysis.ArgumentEffects, tree)
>>> foo, bar = tree.body
>>> ae[foo]
[True, False]
\end{lstlisting}

@@

\begin{lstlisting}
>>> code = '''
def foo(c, d):
    b= c or d ; return b'''
>>> tree = ast.parse(code)
>>> al = pm.gather(analysis.Aliases, tree)
>>> returned = tree.body[-1].body[-1].value
>>> print ast.dump(returned)
Name(id='b', ctx=Load())
>>> sorted(a.id for a in al[returned].aliases)
['c', 'd']
\end{lstlisting}

@@

Python Benchmarks is a project that aims at comparing the existing approaches
to speedup numerical computations in Python. Any project can contribute to new
motivated benchmarks, resulting in more than five different tools
beingrepresented. The project and its result are hosted at
\url{https://github.com/numfocus/python-benchmarks}.

Figure~\ref{fig:python-benchmarks} illustrates the result of one of the
benchmark, showing that Pythran performs well compared to existing approaches.
Several other benchmarks are available and are to be shown during the
presentation.

\begin{figure}[ht]
    \vspace{-2em}
    \hspace{-.05\textwidth}
    \includegraphics[width=1.1\textwidth]{rosen_der_logscale}
    \caption{Timings for the \texttt{rosen\_der} function from Python Benchmarks.}
    \label{fig:python-benchmarks}
    \vspace{-2em}
